---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

gistr
=======

<!-- badges: start -->
[![R-CMD-check](https://github.com/ropensci/gistr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/gistr/actions/workflows/R-CMD-check.yaml)
[![cran checks](https://cranchecks.info/badges/worst/gistr)](https://cranchecks.info/pkgs/gistr)
[![codecov.io](https://codecov.io/github/ropensci/gistr/coverage.svg?branch=master)](https://codecov.io/github/ropensci/gistr?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/gistr)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/gistr)](https://cran.r-project.org/package=gistr)
<!-- badges: end -->

`gistr` is a light interface to GitHub's gists for R.

Get started with the docs: https://docs.ropensci.org/gistr

## See also:

* [git2r](https://github.com/ropensci/git2r) an R client for the libgit2 C library by Stefan Widgren
* [gert](https://github.com/r-lib/gert) Simple git client for R by Jeroen Ooms
* [gistfo](https://github.com/MilesMcBain/gistfo) for turning your untitled RStudio tabs into gists!

## Install

Stable version from CRAN

```{r eval=FALSE}
install.packages("gistr")
```

Or dev version from GitHub.

```{r eval=FALSE}
remotes::install_github("ropensci/gistr")
```

```{r}
library("gistr")
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/gistr/issues).
* License: MIT
* Get citation information for `gistr` in R doing `citation(package = 'gistr')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
